Model-Checking Fault-Tolerant Distributed System Implementations

### 2016-11-22 doc/om-paper/paper.tex
paper: some bib entries

\title{Systematic Models for Inductive Verification of Fault-Tolerant Distributed Systems}
\author{Ben and Lee}

@@

\begin{abstract}
  Some abstract.
\end{abstract}

@@

This straightforward approach introduces substantial additional state and nondeterminism, reducing the scalability of model-checking. Modeling faults is particularly expensive given that additional state and nondeterminism is added to each process. These scalability issues are noted throughout the literature. For example, \lee{TTA startup paper, helmut's paper, etc.}

@@

\begin{quote}
To achieve the full range of faulty behaviors, it seems that a faulty source should be able to send a different incorrect value to each relay, and this requires n different values. It might seem that we need some additional incorrect values 3 so that faulty relays can exhibit their full range of behaviors. It would certainly be safe to introduce additional values for this purpose, but the performance of model checking is very sensitive to the size of the state space, so there is a countervailing argument against introducing additional values. A little thought will show that the way faulty relays have their most significant impact is by tipping the majority vote in a receiver one way or the other, and this can only be achieved if they use the same values as nonfaulty relays. Hence, we decide against further extension to the range of values~\cite{}.
\end{quote}

@@

$OM(1)$ is designed to preserve \emph{validity} and \emph{agreement}
properties. Validity states that if the general is non-faulty, then every lieutenant outputs the value sent by the general. More formally, let the general broadcast $v$, and let $l_i$ denote the output for lieutenant $i$:
%
\begin{equation}
  \tag{Validity}
    \forall \,i. \quad l_i = v
\end{equation}
%
Agreement states that each lieutenant outputs the same value. Let $l_i, l_j$ denote the outputs of lieutenants $i, j \in L$, respectively:
%
\begin{equation}
  \tag{Agreement}
    \forall \,i, j. \quad l_i = l_j
\end{equation}
%

@@

The fault model of $OM(1)$ has been extended to hybrid fault model described in Section~\ref{sec:kibitzer}. Under that fault model, the hypothesis for proving validity and agreement can be weakened to assuming there must be at least $2a+2s+b+1

@@

% ------------------------------------------------------------
\section{Toward an Architectural Domain-Specific Language}\label{sec:adsl}

% ------------------------------------------------------------
\section{Related Work}\label{sec:related}
\lee{talk about om1 verification, comparing it to others.}

>>>>

\title{Model-Checking Fault-Tolerant Distributed System Implementations}
\author{Ben and Lee}

@@

\begin{abstract}
We present a modeling framework for fault-tolerant distributed system verification.
\end{abstract}

@@

%% This straightforward approach introduces additional state and nondeterminism, reducing the scalability of model-checking. Modeling faults is particularly expensive given that additional state and nondeterminism is added to each process. These scalability issues are noted throughout the literature. For example, \lee{TTA startup paper, helmut's paper, etc.}

@@

\begin{quote}
To achieve the full range of faulty behaviors, it seems that a faulty source should be able to send a \emph{different} incorrect value to each relay, and this requires $n$ different values. It might seem that we need some additional incorrect values so that faulty relays can exhibit their full range of behaviors. It would certainly be safe to introduce additional values for this purpose, but the performance of model checking is very sensitive to the size of the state space, so there is a countervailing argument against introducing additional values. A little thought will show that the way faulty relays have their most significant impact is by tipping the majority vote in a receiver one way or the other, and this can only be achieved if they use the same values as nonfaulty relays. Hence, we decide against further extension to the range of values~\cite{}.
\end{quote}

@@

OM(1) is designed to preserve \emph{validity} and \emph{agreement}
properties. Validity states that if the general is non-faulty, then every lieutenant outputs the value sent by the general. More formally, let the general broadcast $v$, and let $l_i$ denote the output for lieutenant $i$:
%
\begin{equation}
  \tag{Validity}
    \forall \,i. \quad l_i = v
\end{equation}
%
Agreement states that each lieutenant outputs the same value. Let $l_i, l_j$ denote the outputs of lieutenants $i, j \in L$, respectively:
%
\begin{equation}
  \tag{Agreement}
    \forall \,i, j. \quad l_i = l_j
\end{equation}
%

@@

The fault model of $OM(1)$ has been extended to hybrid fault model described in Section~\ref{sec:kibitzer}. Under that fault model, the hypothesis for proving validity and agreement can be weakened to assuming there must be at least $2a+2s+b+1$ nodes, where $a$ is the number of Byzantine (or asymmetric) faults, $s$ is the number of symmetric faults, and $b$ is the number of benign faults. \lee{is the right?}

@@

% ------------------------------------------------------------
\section{Toward an Architectural Domain-Specific Language}\label{sec:adsl}
Not sure if we'll have space for this. Maybe just move to the conclusions?

% ------------------------------------------------------------
\section{Related Work}\label{sec:related}

There is a long history of formally verifying fault-tolerant distributed systems. Most previous work has used mechanical theorem-proving, given the complexity of these systems and models. OM(1) is a particularly good case-study that has a history of verification. Most
